Bounded Model Checking for Embedded Systems \\ (Position Paper)

### 2016-03-18 paper.tex
include new reference

Generally, embedded computer systems perform dedicated functions with high degree of reliability. They are used in a variety of sophisticated applications, which range from entertainment software, such as games and graphics animation, to safety-critical systems, such as nuclear reactors and automotive controllers~\cite{Kopetz11}. Embedded systems are ubiquitous, in modern day information systems, and are also becoming increasingly important in our society, especially in micro-grids, where reliability and carbon emission reduction are of paramount importance, and in cyber-physical systems (CPS), which demand short development cycles and again high-level of reliability~\cite{leeCPS,leeCPS2}. As a consequence, human life has also become more and more dependent on the services provided by this type of system and, in particular, their success is strictly related to both service relevance and quality.

@@

>>>>

Generally, embedded computer systems perform dedicated functions with high degree of reliability. They are used in a variety of sophisticated applications, which range from entertainment software, such as games and graphics animation, to safety-critical systems, such as nuclear reactors and automotive controllers~\cite{Kopetz11}. Embedded systems are ubiquitous, in modern day information systems, and are also becoming increasingly important in our society, especially in micro-grids, where reliability and carbon emission reduction are of paramount importance~\cite{xu15}, and in cyber-physical systems (CPS), which demand short development cycles and again high-level of reliability~\cite{leeCPS,leeCPS2}. As a consequence, human life has also become more and more dependent on the services provided by this type of system and, in particular, their success is strictly related to both service relevance and quality.

@@

\bibitem{xu15}
Xua X., Jiaa H., Wanga D., Yub D., Chiangc H.:
\newblock {\em Hierarchical energy management system for multi-source multi-product microgrids}
\newblock In: Renewable Energy, v. 78, pp. 621-–630, 2015.
